\documentclass[11pt]{article}
\usepackage[ngerman]{babel}
\usepackage[left=2cm,right=2cm]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{thmtools}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[]{algorithm2e}
\newcommand{\numpy}{{\tt numpy}}    % tt font for numpy

\topmargin -.5in
\textheight 9in
\oddsidemargin -.25in
\evensidemargin -.25in
\textwidth 7in

\begin{document}
	
	% ========== Edit your name here
	\title{\textbf{Cryptography Exercise Sheet 6}}
	\author{Prof. Dr. Thomas Wilke, Dr.-Ing. Kim-Manuel Klein}
	\maketitle
	\medskip
	
	% ========== Begin answering questions here
	\begin{enumerate}
		
		\item
		\textbf{Problem:} \textit{The 802.11b insecure Mac (Exercise 6.1 in BS)}
		
		Consider the following MAC (a variant of this was used for
		WiFi encryption in 802.11b WEP). Let \textit{F} be a PRF defined over $(\mathcal{K}, \mathcal{R}, \mathcal{X})$ where $\mathcal{X}$ := $\{0, 1\}^{32}$. Let CRC32 be a simple and popular error-detecting code meant to detect random errors; CRC32 is
		a function that takes as input $m \in \{0,1\}^{\leq\ell} $ and outputs a 32-bit string. Define the following MAC
		system \textit{(S, V)}:
		
		\begin{center}
		     	$S(k,m):=\big\{$ $r \xleftarrow{\text{R}} \mathcal{R}$, $ t \xleftarrow{} F(k,r)$ $\oplus$ CRC32($m$), output(r,t) $\big\}$\newline
			$V(k,m, (r,t)):=\big\{$ {\bf accept} if $t = F(k,r)$ $\oplus$ CRC32($m$) and {\bf reject} otherwise $\big\}$
		\end{center}
	
	Show that this MAC system is insecure.
	
		\item
        \textbf{Problem:} \textit{MAC combiners (Exercise 6.5 in BS)}
        
      We want to build a MAC system $\mathcal{I}$ using two MAC systems $\mathcal{I}_1 = (S_1 , V_1 )$
      and $\mathcal{I}_2 = (S_2 , V_2 )$, so that if at some time one of $\mathcal{I}_1$ or $\mathcal{I}_2$ is broken (but not both) then $\mathcal{I}$ is still secure. Put another way, we want to construct $\mathcal{I}$ from $\mathcal{I}_1$ and $\mathcal{I}_2$ such that $\mathcal{I}$ is secure if either $\mathcal{I}_2$ or $\mathcal{I}_2$ is secure.
      
      \begin{enumerate}
      	\item Define $\mathcal{I} = (S,V)$, where
      		\begin{center}
      			$S((k_1, k_2), m):= ((S_1(k_1,m), S_2(k_2,m))$,
      		\end{center}
      	and $V$ is defined in the obvious way: on input $(k, m, (t_1 , t_2 ))$, $V$ accepts iff both $V_1 (k_1 , m, t_1 )$
      	and $V_2 (k_2 , m, t_2 )$ accept. Show that $\mathcal{I}$ is secure if either $\mathcal{I}_1$ or $\mathcal{I}_2$ is secure.
      	
      	\item Suppose that $\mathcal{I}_1$ and $\mathcal{I}_2$ are deterministic MAC systems (see the definition on page 214), and
      	that both have tag space $\{0, 1\}^n$ . Define the deterministic MAC system $\mathcal{I} = (S, V )$, where
      	\begin{center}
      		$S( (k_1 , k_2 ), m) := S 1 (k_1 , m) $ $\oplus$ $ S_2 (k_2 , m)$.
      	\end{center}
      
      	Show that $\mathcal{I}$ is secure if either $\mathcal{I}_1$ or $\mathcal{I}_2$ is secure.
      	
      \end{enumerate}
	\end{enumerate}
	
\end{document}
\grid
\grid